Setting up Data

### 2020-01-31 doc/Bivalent_Analysis.Rmd
small bit of work

load(file="data/MLH1/MLH1_data_setup_11.12.19.RData")#added batch17
#fyi loading mulitple RData files doesn't earase ther files -- but it can overwrite files named the same thing

>>>>

#load(file="data/MLH1/MLH1_data_setup_11.12.19.RData")#added batch17
#fyi loading mulitple RData files doesn't earase ther files -- but it can overwrite files named the same thing

### 2020-01-31 doc/Main_Report_Results.rmd
small bit of work

#setwd("~./MLH1repo/doc/")
setwd("C:/Users/alpeterson7/Documents/MLH1repo/doc/")
#setwd("C:/Users/April/Desktop/MLH1repo")
#load(file="data/MLH1/MLH1_data_setup.RData")

#load main data file
load(file="C:/Users/alpeterson7/Documents/MLH1repo/data/MLH1/MLH1_data_setup_1.5.20.RData")#added batch18

load(file="C:/Users/alpeterson7/Documents/MLH1repo/data/CleanBivData_1.28.20.RData")

@@

$$mouse .cV CO ~=~ subsp * sex + rand(strain*sex)+ \varepsilon$$

```{r cV.model.setup, echo=FALSE}
#modeling within mouse variance

DF.HetC.MixedModel.HQ$var <-  as.numeric(DF.HetC.MixedModel.HQ$var)

#HQ var.CO
HetC.MixedModel.HQ.var_co <- lme(cV ~ subsp * sex, data=DF.HetC.MixedModel.HQ, random=list(strain=pdDiag(~sex) ) )

@@

as.data.frame( round(summary(HetC.MixedModel.HQ.var_co)$tTable, 6))

@@

>>>>

setwd("~./MLH1repo/")

load(file="~./MLH1repo/data/MLH1_data_setup_1.5.20.RData")
load(file="/data/CleanBivData_1.28.20.RData")

#setwd("~./MLH1repo/doc/")
#setwd("C:/Users/alpeterson7/Documents/MLH1repo/doc/")
#setwd("C:/Users/April/Documents/MLH1repo")
#load(file="data/MLH1/MLH1_data_setup.RData")

#load main data file
#load(file="C:/Users/April/Documents/MLH1repo/data/MLH1/MLH1_data_setup_1.5.20.RData")#added batch18
#load(file="C:/Users/April/Documents/MLH1repo/data/CleanBivData_1.28.20.RData")
#load(file="C:/Users/alpeterson7/Documents/MLH1repo/data/CleanBivData_1.28.20.RData")

@@

$$mouse .var CO ~=~ subsp * sex + rand(strain*sex)+ \varepsilon$$

```{r M1.var, echo=FALSE}
#modeling within mouse variance
#use  DF.HetC.MixedModel.HQ

#HQ var.CO
M1.var_co <- lme( var ~ subsp * sex, data=DF.HetC.MixedModel.HQ, random=list(strain=pdDiag(~sex) ) )

@@

as.data.frame( round(summary(M1.var_co)$tTable, 6))

@@

```{r M1.Q12_table, echo=FALSE}
#use the Q1Q2 calq'd table

#Q12_mouse_table_w.Ages$subsp <- ifelse(grepl(1, Q12_mouse_table_w.Ages$subsp), "Dom", 
#        ifelse(grepl(2, Q12_mouse_table_w.Ages$subsp), "Musc", Q12_mouse_table_w.Ages$subsp))

#DF.HetC.MixedModel.HQ <- DF.HetC.MixedModel.HQ[!(is.na(DF.HetC.MixedModel.HQ$mouse) | #DF.HetC.MixedModel.HQ$mouse==""), ]

Q12_mouse_table_w.Ages <- add_subsp(Q12_mouse_table_w.Ages)

Q12_mouse_table_w.Ages$subsp <- ifelse(grepl("MSM", Q12_mouse_table_w.Ages$strain), "Mol", 
        ifelse(grepl("MOLF", Q12_mouse_table_w.Ages$strain), "Mol", NA))

#Q12_mouse_table_w.Ages

M1.Q12_var_co <- lme( var ~ subsp * sex, data=Q12_mouse_table_w.Ages, random=list(strain=pdDiag(~sex) ) )

as.data.frame( round(summary(M1.Q12_var_co)$tTable, 6))

### 2020-01-31 src/SetupData.Rmd
small bit of work

>>>>

```{r Q1Q2.mouse.table, echo=FALSE}

#Make a mouse level table
Q12_mouse_table <- ddply(MLH1_data[MLH1_data$quality < 3,], c("mouse"), summarise,

                        Nmice = length(unique(mouse)),
                        Ncells  = length(adj_nMLH1.foci),
                        mean_co = as.numeric(format(round(  mean(adj_nMLH1.foci), 3 ), nsmall=3) ),
                        cV = cv(adj_nMLH1.foci),
                        var = as.numeric(format(round(   var(adj_nMLH1.foci),3), nsmall=3)),
                        sd   = round(sd(adj_nMLH1.foci), 3),
                        se   = round(sd / sqrt(Ncells), 3)
                        #quality?
)

#REMOVE mice with fewer than 3 cells
Q12_mouse_table <- Q12_mouse_table[Q12_mouse_table$Ncells > 3,]

Q12_mouse_table <- add_strain(Q12_mouse_table)
Q12_mouse_table <- add_subsp(Q12_mouse_table)
Q12_mouse_table <- add_sex(Q12_mouse_table)
Q12_mouse_table <- add_category(Q12_mouse_table)

#use things from prv block
#mice.frm.meta 
#meta.data
#mouse.table_w.Ages

#MERGE HERE
Q12_mouse_table_w.Ages <- merge(Q12_mouse_table, meta.data, by.y = "mouse", by.x = "mouse", all = TRUE)
#what are the differences between these two

#remove the NAs
Q12_mouse_table_w.Ages <- Q12_mouse_table_w.Ages[!(is.na(Q12_mouse_table_w.Ages$category.x) | Q12_mouse_table_w.Ages$category.x==""), ]

#CLEAN up and format for mixed models
Q12_mouse_table_w.Ages <- subset(Q12_mouse_table_w.Ages, select= -c(sex.y,sex.x,
                            subsp.y,subsp.x,
                    category.y,category.x, strain.x,
                    strain.y, mouse.1  )  )

Q12_mouse_table_w.Ages <- add_strain(Q12_mouse_table_w.Ages)
Q12_mouse_table_w.Ages <- add_subsp(Q12_mouse_table_w.Ages)
Q12_mouse_table_w.Ages <- add_sex(Q12_mouse_table_w.Ages)
Q12_mouse_table_w.Ages <- add_category(Q12_mouse_table_w.Ages)

Q12_mouse_table_w.Ages <- add_species(Q12_mouse_table_w.Ages)
Q12_mouse_table_w.Ages <- Q12_mouse_table_w.Ages[Q12_mouse_table_w.Ages$species == "M.musculus",]

#REMOVE EXTRA STRAINS
Q12_mouse_table_w.Ages <- Q12_mouse_table_w.Ages[Q12_mouse_table_w.Ages$subsp != "Cast",]
#remove musc strains
Q12_mouse_table_w.Ages <- Q12_mouse_table_w.Ages[Q12_mouse_table_w.Ages$strain != "AST",]
Q12_mouse_table_w.Ages <- Q12_mouse_table_w.Ages[Q12_mouse_table_w.Ages$strain != "TOM",]
#remove PERC, MOLF, CZECH, (no females)
Q12_mouse_table_w.Ages <- Q12_mouse_table_w.Ages[Q12_mouse_table_w.Ages$strain != "CZECH",]
Q12_mouse_table_w.Ages <- Q12_mouse_table_w.Ages[Q12_mouse_table_w.Ages$strain != "PERC",]

#REMOVE WRONG AGES
#afriad this is removing NA's
Q12_mouse_table_w.Ages <- Q12_mouse_table_w.Ages[( (Q12_mouse_table_w.Ages$age.weeks < 25) &  (Q12_mouse_table_w.Ages$age.days != 13) ) | is.na(Q12_mouse_table_w.Ages$age.weeks), ] #keeps mice without ages, and removes juvinilles

#MOL = subsp
Q12_mouse_table_w.Ages$subsp <- ifelse(grepl("MSM", Q12_mouse_table_w.Ages$strain), "Mol", 
        ifelse(grepl("MOLF", Q12_mouse_table_w.Ages$strain), "Mol", Q12_mouse_table_w.Ages$subsp))

#unclass order factors
#main df with variables coded as chr
Q12_mouse_table_w.Ages$subsp <- factor(Q12_mouse_table_w.Ages$subsp, ordered = FALSE)
Q12_mouse_table_w.Ages$sex <- factor(Q12_mouse_table_w.Ages$sex, ordered = FALSE)
Q12_mouse_table_w.Ages$strain <- factor(Q12_mouse_table_w.Ages$strain, ordered = FALSE)
Q12_mouse_table_w.Ages$species <- factor(Q12_mouse_table_w.Ages$species, ordered = FALSE)
